HMM

### 2015-11-13 paper3.Rnw
have to make reproducible plots now

HMMs have typically been used to model movements over short time
scales, where the probability of switching between movement states stays
relatively constant; changes in behavioural mode switching based on
the local environment can be accounted for incorporating environmental
covariates in the HMM \citep{patterson_classifying_2009}, or by more
\emph{ad hoc} comparisons between inferred state and environmental
conditions \citep{fryxell_multiple_2008}. \todo{I \emph{think} Fryxell
  et al use ad hoc rather than formal methods for their environment
  comparison? check this ...}  \cite{schliehe-diecks_application_2012}
consider changes in switching behaviour over time scales of six-hour
observation periods, but
in general ecologists have used other tools to describe behavioural
changes over longer (diurnal, seasonal, or ontogenetic) time scales.
\todo{Fleming et al Am Nat 2014?  Gurarie?}

>>>>

HMMs have typically been used to model movements over short time
scales, where the probability of switching between movement states stays
relatively constant; changes in behavioural mode switching based on
the local environment can be accounted for incorporating environmental
covariates in the HMM \citep{patterson_classifying_2009}, or by more
\emph{ad hoc} comparisons between inferred state and environmental
conditions \citep{fryxell_multiple_2008}.\cite{schliehe-diecks_application_2012}
consider changes in switching behaviour over time scales of six-hour
observation periods, but
in general ecologists have used other tools to describe behavioural
changes over longer (diurnal, seasonal, or ontogenetic) time scales.
\todo{Fleming et al Am Nat 2014?  Gurarie?}
